% !TEX program = pdflatex

% Adapted from https://github.com/sb2nov/resume

\documentclass[letterpaper,11pt]{article}

\usepackage{lmodern}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeHeading}[4]{
  \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}
  }

\newcommand{\resumeSubheading}[4]{
  \vspace{5pt}
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}
}

\newenvironment{resumeList}{\begin{itemize}[leftmargin=*]}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeItem}[1]{
  \item\small{
      #1 \vspace{-4pt}
  }
}

\newcommand{\resumeTitledItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\renewcommand{\labelitemii}{$\circ$}


%-------------------------------------------


\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://brxck.dev/}{\Large Brock McElroy}} & Email : \href{mailto:brxck@protonmail.com}{brxck@protonmail.com}\\
  \href{https://brxck.dev/}{https://brxck.dev/} & Mobile : \href{tel:14804277830}{+1-480-427-7830} \\
\end{tabular*}


\section{Experience}
  \resumeSubheading
    {Equips}{Remote}
    {Full Stack Engineer}{Jul. 2021 | Present}
    \begin{resumeList}
      \resumeItem
        {Design and implement new features using TypeScript, React, GraphQL, and AWS DynamoDB}
      \resumeItem
        {Created homepage dashboard to present customers concise views of essential info}
      \resumeItem
        {Architected the replatform of the Equips GraphQL API using PostgreSQL and GraphQL Nexus}
    \end{resumeList}

  \resumeSubheading
    {University of Arizona | Financial Services}{Tucson, AZ}
    {Applications Systems Analyst/Developer}{Jul. 2019 | Jul. 2021}
    \begin{resumeList}
      \resumeItem
        {Lead development team in the design, development, and deployment of Python and JavaScript web applications}
      \resumeItem
        {Reimplemented the university's \href{https://tuitioncalculator.fso.arizona.edu}{Tuition Calculator} to better accommodate an increasingly complex tuition structure}
      \resumeItem
        {Led design and development of a new application to manage and automate the creation of tuition rates (up to 15,000 per year), resulting in the fastest ever turnaround of a semester's tuition}
      \resumeItem
        {Rewrote Django applications using AWS Lambda serverless functions, reducing hosting costs by over 95\%}
      \resumeItem
        {Developed a drop-in replacement for the legacy purchasing-card audit platform, reducing application response times by 80\% on average}
    \end{resumeList}

  \resumeSubheading
    {2U}{Tucson, AZ}
    {Teaching Assistant | University of Arizona}{May 2019 | Jul. 2020}
    \begin{resumeList}
      \resumeItem
        {Assisted instruction of full-stack web technologies (e.g. React, Express, Node.js, SQL, MongoDB) in a fast-paced, in-person coding bootcamp}
      \resumeItem
        {Prepared and presented lectures on fundamental version control concepts and Git usage}
      \resumeItem
        {Guided students through mock interview code challenges and the approaches to solving them}
      \resumeItem
        {Authored supplemental resource list to guide students toward continued learning after their graduation}
      \resumeItem
        {Provided constructive, motivating feedback on homework to improve student understanding and the resulting code}
    \end{resumeList}


\section{Projects}
  \begin{resumeList}
    \resumeTitledItem{Gojira}
      {A GitHub application which creates an interface between GitHub and Jira issues. Expands issue cross-references and transitions issues via comment or pull request events. Provides a comfortable union between high-level project management items and technical development tasks. Built with TypeScript, Express, and Docker.}
    \resumeTitledItem{\href{https://github.com/brxck/gatsby-starter-stripe}{gatsby-starter-stripe}}
      {An open-source starter for a statically-generated, live-updated, serverless storefront and admin dashboard. Built-in inventory, cart, and checkout is integrated with Stripe for payment processing. Built with Gatsby, React, GraphQL, and AWS Lambda.}
    \resumeTitledItem{\href{https://castaway.by.brxck.dev}{Castaway}}
      {An app to discover, subscribe, and listen to podcasts. Features a responsive podcast player with variable playback speed and progress tracking. Built with Ruby, Rails, Docker, and StimulusJS.}
    \resumeTitledItem{\href{https://brxck.github.io/lizard.js/}{lizard.js}}
      {A configurable, procedurally animated, vector gecko follows the visitor's cursor using only web technologies: JavaScript and HTML Canvas. Vector geometry precludes the need for more complicated inverse kinematic math. Built with Alpine.js and paper.js.}
  \end{resumeList}

\section{Skills}
  \begin{resumeList}
    \resumeTitledItem{Languages}{TypeScript, JavaScript, Python, Ruby, SQL, GraphQL}
    \resumeTitledItem{Technologies}{React, Vue, Django, Rails, Express, AWS, DynamoDB, ElasticSearch, Serverless, Git, GitLab CI}
  \end{resumeList}

\section{Education}
  \resumeSubheading
  {University of Arizona}{Tucson, AZ}
  {Bachelor of Science in Environmental Science}{Aug. 2012 | May 2017}

\end{document}
